\documentclass{article}
\usepackage{markdown}
\begin{document}
\begin{markdown}
# 1st meeting 11/12/24
## Task division:
- Part 1: Joe
- Part 2 - First half: Edd
- Part 2 - Second half: Leo

## Notes
- Previous reports + code can be found under "reference" folder
- Let's try to finish our question by 18th of December. Try to answer the questions as clearly as possible and provide reasonings.

# Meeting 21/12/24

- Inference for stats take-home assignment:
  - All the negative continuous variables have been standardized :)
  - Question 1: Adjust for all covariates in the model.
  - Question 2: Add interaction between past school achievement and treatment to the model to see if it's significant.
  - Question 3: Add interaction between treatment and other covariates. This question boils down to the model-building exercise (cf. the lecture on model building).
- Bayesian data analysis:
  - Joe revise the first model 
  - Leo revise Joe's second model and Ed's Gibb sampler

# Practical info
## Bayesian
https://github.com/LeoLuongVuong/bayesian-data-analysis.git

- To assess the convergence of parameters jointly, one could use multivariate trace plot monitoring the (log) of likelihood or log of the posterior density (Log(posterior)). We don't have to implement this in our report, but should be prepared for questions that may come up. 

- **Calculate shrinkage in Bayesian mixed model**
    - https://www.jstor.org/stable/2669540?seq=6
    
    - chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/https://cran.r-project.org/web/packages/blme/blme.pdf
    
    - https://www.sciencedirect.com/science/article/pii/S0047259X15003309
    
    - https://link.springer.com/article/10.1007/s11634-019-00353-y
    
    - https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-022-01560-6
    
    - https://www.jstor.org/stable/24306765
    
    - https://www.tandfonline.com/doi/abs/10.1080/03610918.2021.2022697
    
    - https://pmc.ncbi.nlm.nih.gov/articles/PMC9559065/


## Advanced modelling
https://github.com/LeoLuongVuong/advanced-modelling-techniques.git
## Inference for stats
https://github.com/LeoLuongVuong/inference_for_stats.git

\end{markdown}
\end{document}



